What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-09 android-stacks.tex
discussion - structue

%\section{Discussions}

>>>>

\section{Discussions}

The exception (mis-)use that emerged from this study shades light on two

It is wise to document the explicitly signaled runtime exceptions as carefully as checked exceptions. Doing so, the clients of a method will be aware of the exceptions the method can throw.

When developer fails to document the runtime exceptions thrown by a method (s)he will make difficult or even impossible for the caller to effective use of such method.

Specially when developing library code, developers must carefully document the runtime exceptions, since there is no compilation checking

have not been fully adopted, mainly there is no compilation or runtime tool to enforce such policies.
noindent\emph{Undocumented runtime exceptions}
